\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\linespread{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Derivation of an SDE system for sunspot activity and SPDEs for 
stock-price distributions, reaction-diffusion problems, and neutron transport}
\newcommand{\talkspeaker}{Edwards Allen, Texas Tech University}
\newcommand{\talkdate}{Wednesday, March 31, 2010}


\newcommand{\talkabstract}{
A procedure is reviewed for deriving stochastic ordinary and partial
differential equations (SDEs) and (SPDEs) for randomly-varying
problems in biology, physics, and finance. The equations are
derived from basic principles, i.e., from the changes in the
system which occur in a small time interval. In the derivation
procedure, a discrete stochastic model is first constructed. As
the time interval decreases, the discrete stochastic model leads
to a system of Ito SDEs. Next, Brownian sheets replace the Wiener
processes and the resulting equations infer an SPDE. Several
examples illustrate the procedure. In particular, a system of SDEs
is derived for sunspot activity and SPDEs are derived for
stock-price distributions, reaction-diffusion problems, and
neutron transport.

AUTHORS: Ed Allen, Elife Dogan, Chisum Huff, Xiaoyi Ji
}

\begin{document}

\thispagestyle{empty}

\begin{center}
Texas Tech University.  Applied Mathematics Seminar.

\end{center}

\begin{center}

\textbf{\LARGE {\uppercase{\talktitle}} }

\talkspeaker

\talkdate

Room: MA 016, Time: 4:00pm

\end{center}

ABSTRACT.
\talkabstract

\end{document}
