\documentclass[oneside]{article}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\usepackage{hyperref}

\usepackage{fancyhdr}

\usepackage[none]{hyphenat} 
\usepackage[left=.75 in,top=.75 in,right=.75 in,bottom=.75 in,nohead]{geometry}

\pagestyle{fancy}
\lfoot{}
\cfoot{\url{http://www.math.ttu.edu/~dacao/AnalysisSeminar}}
%\cfoot{\textit{http:/$\!$/www.math.ttu.edu/$\!$\raise-1ex\hbox{{\Large\texttt{\char`\~}}}lhoang/AppliedMath/}}
\rfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\linespread{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Condenser capacity and holomorphic functions. Part I.}

\newcommand{\talkspeaker}{ \textbf{\sc Stamatis Pouliasis  }\\ \textit{Texas Tech University}}

\newcommand{\talkdate}{\textbf{Monday, February 12, 2018}}

\newcommand{\timelocation}{\textbf{Room: MATH 108.  Time: 4:00 pm.}}

\newcommand{\talkabstract}{
%
}

\begin{document}

%\vspace*{-2cm}
\begin{center}
{\LARGE
Texas Tech University.  Analysis Seminars.
}
\medskip

\textbf{\Huge {\uppercase{\talktitle}} }

{\LARGE
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}


%\addtolength{\linewidth}{-1cm}
\begin{center}

\fbox{\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
{
\vspace*{.25cm}
{\LARGE \textbf{ABSTRACT.}}
{\Large
First we shall present some basic facts about condenser capacity,
the Green function and their relation with holomorphic functions.
Then we will state and prove an inequality for the capacity of a
condenser via a holomorphic function, which takes into account the
valency of the holomorphic function on the positive plate of the
condenser. Also, we will present an equality statement and some
related results. Finally, we will examine the asymptotic behavior
of the capacity of the inverse image of a condenser under exponential
Blaschke products and universal covering maps.
}
\vspace*{.25cm}
}
\end{minipage}
\end{center}
}}

\end{center}
\end{document}
