\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\usepackage[none]{hyphenat} 

\setlength{\hoffset}{-.5in}%{-1in}
\addtolength{\hoffset}{1.5cm}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2\hoffset}
\addtolength{\textwidth}{-2in}

\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2in}%to fix pdf missing footer . old val {-.75in}
\setlength{\oddsidemargin}{-0.75cm}
\setlength{\marginparsep}{0cm}
\setlength{\marginparwidth}{0cm}
\setlength{\marginparpush}{0cm}
\addtolength{\textwidth}{-\oddsidemargin}
\addtolength{\textwidth}{-\marginparsep}
\addtolength{\textwidth}{-\marginparwidth}
\addtolength{\textwidth}{-\marginparpush}


\setlength{\voffset}{-.5in}%{-1in}
\addtolength{\voffset}{1cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2\voffset}
\addtolength{\textheight}{-1in}%to fix pdf missing footer . old val {-.75in}


%\textheight=700pt


\linespread{1.65}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Analysis of High Order FDTD Methods for Maxwell's Equations in 
Dispersive Media}

\newcommand{\talkspeaker}{ {\sc Vrushali Bokil}, \textit{Oregon State University}}

\newcommand{\talkdate}{Thursday, August 25, 2011}

\newcommand{\timelocation}{Room: MATH 010.  Time: 4:00pm.}

\newcommand{\talkabstract}{
We study the stability properties of, and the phase error present in, 
several higher-order (in space) staggered finite difference schemes for 
Maxwell’s equations coupled with a Debye or Lorentz polarization model.We 
present a novel expansion of the symbol of finite difference 
approximations, of arbitrary (even) order, of the first-order spatial 
derivative operator. This alternative representation allows the derivation 
of a concise formula for the numerical dispersion relation for all (even-) 
order schemes applied to each model, including the limiting 
(infinite-order) case. We further derive a closed-form analytical 
stability condition for these schemes as a function of the order of the 
method. Using representative numerical values for the physical parameters, 
we validate the stability criterion while quantifying numerical 
dissipation. Lastly, we demonstrate the effect that the spatial 
discretization order, and the corresponding stability constraint, has on 
the dispersion error.
}

\begin{document}

\thispagestyle{empty}

\begin{center}
{\Large
Texas Tech University.  Joint Applied Mathematics / BioMathematics  Seminar.
}
\medskip

\textbf{\Huge {\uppercase{\talktitle}} }

{\Large
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}


%\addtolength{\linewidth}{-1cm}
\begin{center}

\fbox{\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
{
\vspace*{.25cm}
{\LARGE \textbf{ABSTRACT.}}
{\huge \talkabstract}
\vspace*{.25cm}
}
\end{minipage}
\end{center}
}}

\end{center}
\end{document}
