\documentclass[oneside]{article}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm,amsmath}

\usepackage{hyperref}

\usepackage{fancyhdr}

\usepackage[none]{hyphenat} 
\usepackage[left=.75 in,top=.75 in,right=.75 in,bottom=.75 in,nohead]{geometry}

\pagestyle{fancy}
\lfoot{}
\cfoot{\url{http://www.math.ttu.edu/~lhoang/AnalysisSeminar/}}
%\cfoot{\textit{http:/$\!$/www.math.ttu.edu/$\!$\raise-1ex\hbox{{\Large\texttt{\char`\~}}}lhoang/AppliedMath/}}
\rfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}

\linespread{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Weighted gradient estimates of solutions to degenerate and singular elliptic equations. Part I.}

\newcommand{\talkspeaker}{ \textbf{\sc Dat Cao}\\ \textit{Texas Tech University}}

\newcommand{\talkdate}{\textbf{Monday, March 27, 2017}}

\newcommand{\timelocation}{\textbf{Room: MATH 010.  Time: 4:00pm.}}


\newcommand{\wei}[1]{\langle #1 \rangle}

\newcommand{\talkabstract}{
{\Large We study the weight-$W^{1,p}$ estimates of weak solutions to the equation
$$
\left\{
\begin{array}{cccl}
{\rm div} [\mathbb{A}(x)\nabla u] & = & {\rm div}[{\bf F}] &\quad \text{in} \quad \Omega,\\
 u & = &0 & \quad \text{on} \quad \partial\Omega,
 \end{array}
\right.
$$
where  $\Omega \subset \mathbb{R}^n$ is an open bounded domain, ${\bf F}:\Omega\to\mathbb{R}^{n}$ is a given vector field, and the coefficient matrix  $\mathbb{A}: \mathbb{R}^{n}\to\mathbb{R}^{n\times n}$ is  symmetric, measurable,  and satisfying the degenerate/singular elliptic condition:
$$
\Lambda \mu(x) |\xi|^2 \leq \langle \mathbb{A}(x) \xi, \xi \rangle \leq \Lambda^{-1} \mu(x) |\xi|^2, \quad \forall \ \xi \in \mathbb{R}^n, \quad \text{a.e.} \quad x \in \mathbb{R}^n,
$$
with fixed  $\Lambda >0$, and a non-negative weight $\mu$ in some Muckenhoupt class.}\\

{\Large 
We obtain weighted estimates of solutions under a smallness condition on the mean oscillation of the coefficients with the weight $\mu$ and a flatness condition on the boundary of the domain $\Omega$.}\\

{\Large 
This is a joint work with Tadele Mengesha (University of Tennessee) and Tuoc Phan (University of Tennessee).}

}
%


\begin{document}
\begin{center}
{\LARGE
Texas Tech University.  Analysis Seminars.
}
\medskip

\textbf{\Huge \uppercase{\talktitle} }

{\LARGE
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}

\begin{center}

\fbox{
\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
\vspace*{.25cm}
{\LARGE \textbf{ABSTRACT.}}
\talkabstract
\vspace*{.25cm}
\end{minipage}
\end{center}
}%parbox
}%fbox

\end{center}
\end{document}
