\documentclass[oneside,11pt]{article}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm,amsmath}

\usepackage{hyperref}

\usepackage{fancyhdr}

\usepackage[none]{hyphenat} 
\usepackage[left=.75 in,top=.75 in,right=.75 in,bottom=.75 in,nohead]{geometry}

\pagestyle{fancy}
\lfoot{}
\cfoot{\url{http://www.math.ttu.edu/~lhoang/AnalysisSeminar/}}
%\cfoot{\textit{http:/$\!$/www.math.ttu.edu/$\!$\raise-1ex\hbox{{\Large\texttt{\char`\~}}}lhoang/AppliedMath/}}
\rfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}

%\linespread{1.3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Analytic continuation of Laurent series  to
domains of minimal capacity}

\newcommand{\talkspeaker}{ \textbf{\sc Wei Zhang}\\ \textit{Texas Tech University}}

\newcommand{\talkdate}{\textbf{Monday, April 24, 2017}}

\newcommand{\timelocation}{\textbf{Room: MATH 010.  Time: 4:00pm.}}


\newcommand{\wei}[1]{\langle #1 \rangle}

\newcommand{\talkabstract}{
Let   $f(z)$ be a  function defined by
Laurent series %
$$ %\begin{equation} %$$ %
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ f(z)=\sum_{k=-\infty}^\infty a_k
z^k, {\mbox{\hspace{4cm} (1)}}
$$ %\end{equation} %$$ %
which is analytic  on the unit circle $\mathbb{T}$. By the
classical theorem of Pierre Alphonse Laurent (1843), the series
(1) converges %(and therefore defines $f(z)$)
on an annulus $A(r,R)=\{z:\, r<|z|<R\}$ with some $r$ and $R$,
$0\le r<1<R\le \infty$, and diverges for all $z\in
\overline{\mathbb{C}}\setminus \overline{A(r,R)}$. It is also
well-known that often the function $f(z)$ defined by the series
(1) can be analytically/meromorphycally  continued to a larger
domain $D\supset A(r,R)$.  The primary goal of this project is to
study \emph{the largest domains} $D \subset
\overline{\mathbb{C}}$, to which the function $f$ can be extended
as a single-valued meromorphic function. To clarify the term
``largest'', we note that the complement
$\overline{\mathbb{C}}\setminus D$ consists of two parts:
$E_0=\{z\not\in D:\, |z|\ge R\}$ and $E_1=\{z\not\in D:\, |z|\le
r\}$. If $E_0$ and $E_1$ both are not empty, then the domain $D$
can be considered as a field of the condenser $(D,E_0,E_1)$ with
plates $E_0$ and $E_1$. Precisely, we want to identify all domains
$D$ to which the series (1) can be continued meromorphically and
such that the corresponding condensers $(D,E_0,E_1)$ have the
\textbf{minimal possible capacity}. The capacity of a condenser
can be defined as the minimum of the Dirichlet integral; i.e.,
$$ %
{\mbox{cap}}(D)=\inf \int_D|\nabla u|^2\,dA,
$$ %
where the infimum is taken over all functions $u\in Lip(D)$ such
that $u=0$ on $E_0$ and $u=1$ on $E_1$.

\vspace*{1em}
\indent This project can be thought as an extension of recent work of Prof. H.~Stahl
who studied meromorphic extensions of Taylor series at $z=\infty$ to domains $D\ni \infty$
with minimal logarithmic capacity of their complement $\mathbb{C}\setminus D$.

\vspace*{1em}
\indent In the first part of my talk, I will introduce our main problem
and discuss several examples illustrating main ideas and concepts.
Then I will present an existence theorem for extremal condensers
and give a sketch of its proof. Also, a uniqueness theorem for
extremal domains will be discussed. Finally, the topological
structure of complementary sets (or plates) $E_0$ and $E_1$ of the
condensers of minimal capacity will be discussed  and analytic
tools needed for their characterization will be  presented.
}
%


\begin{document}
\begin{center}
{\LARGE
Texas Tech University.  Analysis Seminars.
}
\medskip

\textbf{\Huge \uppercase{\talktitle} }

{\LARGE
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}

\begin{center}

\fbox{
\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
\vspace*{.25cm}
{\LARGE \textbf{ABSTRACT.}}
\talkabstract
\vspace*{.25cm}
\end{minipage}
\end{center}
}%parbox
}%fbox

\end{center}
\end{document}
