\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\usepackage[none]{hyphenat} 

\setlength{\hoffset}{-.5in}%{-1in}
\addtolength{\hoffset}{1.5cm}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2\hoffset}
\addtolength{\textwidth}{-2in}

\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2in}%to fix pdf missing footer . old val {-.75in}
\setlength{\oddsidemargin}{-0.75cm}
\setlength{\marginparsep}{0cm}
\setlength{\marginparwidth}{0cm}
\setlength{\marginparpush}{0cm}
\addtolength{\textwidth}{-\oddsidemargin}
\addtolength{\textwidth}{-\marginparsep}
\addtolength{\textwidth}{-\marginparwidth}
\addtolength{\textwidth}{-\marginparpush}


\setlength{\voffset}{-.5in}%{-1in}
\addtolength{\voffset}{1cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2\voffset}
\addtolength{\textheight}{-1in}%to fix pdf missing footer . old val {-.75in}


%\textheight=700pt


\linespread{1.65}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Structural Stability of Generalized Forchheimer Flows of Any Degree}

\newcommand{\talkspeaker}{ {\sc Thinh T. Kieu}\\ \textit{Texas Tech University}}

\newcommand{\talkdate}{Wednesday, March 27, 2013}

\newcommand{\timelocation}{Room: MATH 011.  Time: 4:00pm.}

\newcommand{\talkabstract}{
We study the generalized Forchheimer equations for slightly compressible fluids in porous media with Dirichlet boundary data. 
The Forchheimer polynomial has arbitrarily large degree.
We prove that the solution depends continuously on the coefficients of the Forchheimer polynomial in $L^\alpha$-norm  and $W^{1,2-a}$-norm for  both finite time intervals and time infinity. Here, $\alpha\ge 1$ is arbitrary, and number $a\in(0,1)$ depends on the degree of the Forchheimer polynomial.
The stability is established by using a perturbed monotonicity and the structure of the equation to treat the cross-terms $|\nabla p_1|^{2-a}|\bar{p}_2|^{\alpha-2}$ and $|\nabla p_2|^{2-a}| \bar{p}_1|^{\alpha-2}$ of individual solutions $p_1$ and $p_2$. New Poincar\'e-Sobolev inequalities and non-linear Gronwall-type estimates for non-linear differential inequalities are utilized to derive the asymptotic bounds  for mixed terms. 
This is joint work with Luan Hoang, Akif Ibragimov and Zeev Sobol.
}

\begin{document}

\thispagestyle{empty}

\begin{center}
{\Large
Texas Tech University.  Applied Mathematics Seminar.
}
\medskip

\textbf{\Huge {\uppercase{\talktitle}} }

{\Large
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}


%\addtolength{\linewidth}{-1cm}
\begin{center}

\fbox{\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
{
\vspace*{.25cm}
{\LARGE \textbf{ABSTRACT.}}
{\huge \talkabstract}
\vspace*{.25cm}
}
\end{minipage}
\end{center}
}}

\end{center}
\end{document}
