\documentclass[oneside]{article}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\usepackage{hyperref}

\usepackage{fancyhdr}

\usepackage[none]{hyphenat} 
\usepackage[left=.75 in,top=.75 in,right=.75 in,bottom=.75 in,nohead]{geometry}

\pagestyle{fancy}
\lfoot{}
\cfoot{\url{http://www.math.ttu.edu/~dacao/AnalysisSeminar}}
%\cfoot{\textit{http:/$\!$/www.math.ttu.edu/$\!$\raise-1ex\hbox{{\Large\texttt{\char`\~}}}lhoang/AppliedMath/}}
\rfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\linespread{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Global well-posedness for the stochastic non-Newtonian fluid equations and convergence to the Navier-Stokes equations.}

\newcommand{\talkspeaker}{ \textbf{\sc Phuong Nguyen }\\ \textit{Texas Tech University}}

\newcommand{\talkdate}{\textbf{Monday, March 04, 2019}}

\newcommand{\timelocation}{\textbf{Room: MATH 112.  Time: 4:00pm.}}

\newcommand{\talkabstract}{
%
}

\begin{document}

%\vspace*{-2cm}
\begin{center}
{\LARGE
Texas Tech University.  Analysis Seminars.
}
\medskip

\textbf{\Huge {\uppercase{\talktitle}} }

{\LARGE
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}


%\addtolength{\linewidth}{-1cm}
\begin{center}

\fbox{\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
{
\vspace*{.25cm}
{\LARGE \textbf{ABSTRACT.}}
{\Large 
I will deliver my talk in two sessions. The first part contains motivation and preliminaries about stochastic partial differential equations. The existence of global pathwise solutions for the stochastic non-Newtonian incompressible fluid equations in space dimension 2 is established in the second session. Moreover, I will show that said solutions converge in probability to the solution of the stochastic Navier-Stokes equations in the appropriate limit. Our approach is based on Galerkin approximation and the theory of martingale solutions.  
}
\vspace*{.25cm}
}
\end{minipage}
\end{center}
}}

\end{center}
\end{document}
