\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\usepackage[none]{hyphenat} 

\setlength{\hoffset}{-.5in}%{-1in}
\addtolength{\hoffset}{1.5cm}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2\hoffset}
\addtolength{\textwidth}{-2in}

\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2in}%to fix pdf missing footer . old val {-.75in}
\setlength{\oddsidemargin}{-0.75cm}
\setlength{\marginparsep}{0cm}
\setlength{\marginparwidth}{0cm}
\setlength{\marginparpush}{0cm}
\addtolength{\textwidth}{-\oddsidemargin}
\addtolength{\textwidth}{-\marginparsep}
\addtolength{\textwidth}{-\marginparwidth}
\addtolength{\textwidth}{-\marginparpush}


\setlength{\voffset}{-.5in}%{-1in}
\addtolength{\voffset}{1cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2\voffset}
\addtolength{\textheight}{-1in}%to fix pdf missing footer . old val {-.75in}


%\textheight=700pt


\linespread{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Ensemble Dynamics and Bred Vectors}
\newcommand{\talkspeaker}{ {\sc George R Sell}, \textit{University of Minnesota}}

\newcommand{\talkdate}{Thursday, April 7, 2011}

\newcommand{\timelocation}{Room: CHEM 113.  Time: 3:30pm.}

\newcommand{\talkabstract}{
%\Large
The concept of a ``bred vector'' dates back to 1993, and Google now
has over 500,000 hits in its data base. Two of these hits are found
under the title of this lecture. On the other hand this concept
has not (as of a week ago) made it into the AMS MathSciNet.
One of the most interesing features about this concept is that it plays a
central and important role in the related areas of dynamical systems
and numerical studies. Nevertheless, the bred vector is a mathematical
orphan.

%\Large
For example, the matter of the sensitivity of model outputs to changes
in the initial conditions for weather forcasting is a topic of
widespread interest. While bred vectors have been accepted as useful
tools in the study of sensitivity, there is a lacking of a sound
theoretical basis for the applications of this concept. In this lecture we 
present some new developments in the theory of bred vectors.

%\Large
By using a new concept of ``ensemble dynamics" we obtain better insights into 
the part to be played by bred vectors in the theory of dynamical
systems. Among other things, we will show how to use ensemble dynamics
to obtain a new point of view of the fractal nature of the Lorenz
attractor.

%\Large
Topics that arise in this lecture include: invariant splittings, such as
exponential dichotomies, and the multiplicative ergodic theorem. We will
also use the Lorenz attractor to motivate one of the basic problems
arising in discrete dynamics: Can one find a proof of the apparent
robustness of the Lorenz attractor?
}

\begin{document}

\thispagestyle{empty}

\begin{center}
{\Large
Texas Tech University.  Department of Mathematics and Statistics. Colloquium.
}
\medskip

\textbf{\Huge {\uppercase{\talktitle}} }

{\Large
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}


%\addtolength{\linewidth}{-1cm}
\begin{center}

\fbox{\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
{
{\LARGE \textbf{ABSTRACT.}}
{\Large \talkabstract}
}
\end{minipage}
\end{center}
%\vspace*{.35cm}
%\vspace*{.35cm}
}}

\end{center}
\end{document}
