\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\textwidth=450pt
\textheight=650pt
\voffset=-1cm
\hoffset=-2.5cm

\linespread{1.75}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Boundary Estimates for Solutions to the Two-Phase Parabolic Obstacle Problem}
\newcommand{\talkspeaker}{ {\sc Darya E.\,Apushkinskaya}, \textit{Saarland University, Saarbr{\"u}cken, Germany}}

\newcommand{\talkdate}{Wednesday, March 30, 2011}

\newcommand{\timelocation}{Room: MATH 016.  Time: 4:00pm.}

\newcommand{\talkabstract}{
{
Consider the two-phase parabolic obstacle problem with non-trivial Dirichlet condition
\begin{align*}
\Delta u-\partial_tu&=\lambda^+\chi_{\{u>0\}}-\lambda^-\chi_{\{u<0\}} \quad
\text{in}\ Q=\Omega \times (0;T),\\
 u&=\varphi \quad \text{on} \quad \partial_p Q.
\end{align*}
Here $T<+\infty$, $\Omega \subset \mathbb{R}^n$ is a given domain, $\partial_PQ$ denotes the parabolic boundary of $Q$, and $\lambda^{\pm}$ are non-negative constants satisfying $\lambda^++\lambda^->0$. The problem arises as limiting case in the model of temperature control through the interior.

In this talk we discuss the $L^{\infty}$-estimates for the second-order space derivatives $D^2u$ near the parabolic boundary $\partial_p Q$. Observe that the case of general Dirichlet data cannot be reduced to zero ones due to non-linearity and discontinuity at $u=0$ of the right-hand side of the first equation.

The lecture is based on works in collaboration with Nina Uraltseva.
}
}
\begin{document}

\thispagestyle{empty}

\begin{center}
Texas Tech University.  Joint Analysis and Applied Mathematics Seminar.
\end{center}

\begin{center}

\textbf{\Huge {\uppercase{\talktitle}} }

{\Large
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}

\fbox{\parbox{\linewidth}{
\vspace*{.35cm}
{\LARGE \textbf{ABSTRACT.}}
{\Large
\talkabstract
}
\vspace*{.35cm}
}}

\end{document}
