\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\usepackage[none]{hyphenat} 

\setlength{\hoffset}{-.5in}%{-1in}
\addtolength{\hoffset}{1.5cm}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2\hoffset}
\addtolength{\textwidth}{-2in}

\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2in}%to fix pdf missing footer . old val {-.75in}
\setlength{\oddsidemargin}{-0.75cm}
\setlength{\marginparsep}{0cm}
\setlength{\marginparwidth}{0cm}
\setlength{\marginparpush}{0cm}
\addtolength{\textwidth}{-\oddsidemargin}
\addtolength{\textwidth}{-\marginparsep}
\addtolength{\textwidth}{-\marginparwidth}
\addtolength{\textwidth}{-\marginparpush}


\setlength{\voffset}{-.5in}%{-1in}
\addtolength{\voffset}{1cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2\voffset}
\addtolength{\textheight}{-1in}%to fix pdf missing footer . old val {-.75in}


%\textheight=700pt


\linespread{1.65}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Orthogonal polynomials in evolutionary theory}

\newcommand{\talkspeaker}{ {\sc Sean H. Rice}, \textit{Texas Tech University}}

\newcommand{\talkdate}{Wednesday, February 15, 2012}

\newcommand{\timelocation}{Room: MATH 016.  Time: 4:00pm.}

\newcommand{\talkabstract}{
I will discuss the application of orthogonal polynomials to problems in evolutionary
biology. We often need to represent some value, such as fitness or offspring phenotype, as
a function of the phenotype of individuals in a population. Standard polynomial regression
will not do in this case, because the regression coefficients are functions of the degree of
the polynomial that we choose to fit. Since this degree is arbitrary, the coefficients of
a standard nonlinear regression do not have any clear biological meaning. The solution
to this problem is to construct a space of orthogonal polynomials that are defined by the
distribution of variation in the population that we are studying. I will show how we construct
such polynomials for both the cases of univariate and multivariate evolution. Multivariate
orthogonal polynomials pose a problem not encountered in the univariate case - the need to
choose an ordering on the variables - that has limited their applicability. I will show how we
get around this problem in the case of evolutionary theory, and how orthogonal polynomials
allow us to solve problems, such as evolution with nonlinear inheritance, that could not be
addressed using traditional quantitative genetics.
}

\begin{document}

\thispagestyle{empty}

\begin{center}
{\Large
Texas Tech University.  Applied Mathematics Seminar.
}
\medskip

\textbf{\Huge {\uppercase{\talktitle}} }

{\Large
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}


%\addtolength{\linewidth}{-1cm}
\begin{center}

\fbox{\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
{
\vspace*{.25cm}
{\LARGE \textbf{ABSTRACT.}}
{\huge \talkabstract}
\vspace*{.25cm}
}
\end{minipage}
\end{center}
}}

\end{center}
\end{document}
