\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\textwidth=450pt
\textheight=600pt
\voffset=-1cm
\hoffset=-2cm

\linespread{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Building a better solver: software engineering aspects of 
high-performance scientific computing. I.}
\newcommand{\talkspeaker}{ {\sc Kevin Long}, \textit{Texas Tech University}}

\newcommand{\talkdate}{Wednesday, February 16, 2011}

\newcommand{\timelocation}{Room: MATH 016.  Time: 4:00pm.}

\newcommand{\talkabstract}{
{\Huge Numerical solution of large systems of linear and nonlinear algebraic 
equations is at the heart of most problems in scientific computing. As we 
attempt to produce simulations of ever greater size and complexity, solver 
algorithms often must be tailored to exploit the structure of a particular 
problem. In such algorithms, each solve may have numerous
intermediate data structures and operations -- including other solves on subproblems -- that 
need to be coordinated. Furthermore, as simulations are being run on 
increasingly complex computer architectures we need to tune our programs to 
those architectures all the while maintaining the flexibility needed for use 
in tailored solvers.}

{\Huge
In this series of talks I'll outline some of the challenges for programming 
solver algorithms. I'll use as a case study the deceptively simple concept of 
programming operations on vectors, and show how we can design  software that 
is easy to understand and use without sacrificing performance and 
flexibility. Along the way you'll meet some nifty programming tricks such as 
factory patterns, expression templates, and lazy evaluation. I'll introduce a 
new software toolkit, Playa (``Painless Linear Algebra''), that embodies these 
ideas. 
}
}
\begin{document}

\thispagestyle{empty}

\begin{center}
Texas Tech University.  Applied Mathematics Seminar.
\end{center}

\begin{center}

\textbf{\Huge {\uppercase{\talktitle}} }

{\Large
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}

{\LARGE
ABSTRACT.}
{\talkabstract}


\end{document}
