\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\linespread{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{
Modeling neutral evolution of Alu elements using a branching process}
\newcommand{\talkspeaker}{Marek Kimmel, Rice University}
\newcommand{\talkdate}{Wednesday, January 27, 2010}


\newcommand{\talkabstract}{
Alu elements occupy about eleven percent of the human genome
and are still growing in copy numbers. Since Alu elements substantially
impact the shape of our genome, there is a need for modeling the
amplification, mutation and selection forces of these elements.
Our proposed theoretical neutral model follows a discrete-time branching
process described by Griffiths and Pakes. From this model, we derive a
limit frequency spectrum of the Alu element distribution, which serves as
the theoretical, neutral frequency to which real Alu insertion data can be
compared through statistical goodness of fit tests. Departures from the
neutral frequency spectrum may indicate selection. A comparison
of the Alu sequence data, obtained by courtesy of Dr. Jerzy Jurka, with
our model shows that the distributions of Alu sequences in the AluY family
systematically deviate from the expected distribution derived from the
branching process. This observation suggests that Alu
sequences do not evolve neutrally and might be under selection.
}

\begin{document}

\thispagestyle{empty}

\begin{center}
Texas Tech University. Joint BioMathematics, Statistics and Applied Mathematics Seminars.

\end{center}

\begin{center}

\textbf{\LARGE {\uppercase{\talktitle}} }

\talkspeaker

\talkdate

Room: Biology 101, Time: 4:00pm

\end{center}

ABSTRACT.
\talkabstract

\end{document}
