\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\usepackage[none]{hyphenat} 

\setlength{\hoffset}{-.5in}%{-1in}
\addtolength{\hoffset}{1.75cm}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2\hoffset}
\addtolength{\textwidth}{-2in}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2in}%to fix pdf missing footer . old val {-.75in}
\setlength{\oddsidemargin}{-0.75cm}
\setlength{\marginparsep}{0cm}
\setlength{\marginparwidth}{0cm}
\setlength{\marginparpush}{0cm}
\addtolength{\textwidth}{-\oddsidemargin}
\addtolength{\textwidth}{-\marginparsep}
\addtolength{\textwidth}{-\marginparwidth}
\addtolength{\textwidth}{-\marginparpush}


\textheight=650pt


\linespread{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Upscaling of fine scale geological models for non-linear flow simulations}
\newcommand{\talkspeaker}{ {\sc Eugenio Aulisa}, \textit{Texas Tech University}}

\newcommand{\talkdate}{Wednesday, April 6, 2011}

\newcommand{\timelocation}{Room: MATH 016.  Time: 4:00pm.}

\newcommand{\talkabstract}{
{
The two term Forchheimer law is considered for incompressible
single-phase steady-state flow filtration in anisotropic heterogeneous porous
media. The resulting system can be rewritten in term of non-linear elliptic
equation for the pressure only characterized by a heterogeneous permeability
tensor depending on the pressure gradient norm. The use of this model in
fine scale geocellular simulator is straightforward, and it would require very
little effort to replace the existing linear models. On the other hand, goecellular 
models typically require $10^7$ -- $10^8$ computational cells, while existing
simulators can handle normally in between $10^5$--$10^6$ cells. A variety of 
approaches for gridding and upscaling of detailed geocellular models have been
introduced for Darcy case spanning from local, extended local, global and
quasi global techniques. All these models aim to replace the permeability
tensors on a fine vertical scale with an equivalent permeability tensor on a
coarse scale. In this work we explore the possibility of extending some of the
upscaling models to the non-linear Forchheimer law. A flow-based coarsening
approach is used, where the equivalent permeability tensor is first evaluated
following the streamline of the existing linear cases, and successively modified
in order to take into account the non-linear effects. Coarse scale simulation
results are presented. These illustrate the capabilities of non-linear upscaling
procedures and demonstrate the levels of accuracy attainable using the various
approaches.
}
}
\begin{document}

\thispagestyle{empty}

\begin{center}
{\Large
Texas Tech University.  Applied Mathematics Seminar.
}
\end{center}

\begin{center}

\textbf{\Huge {\uppercase{\talktitle}} }

{\Large
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}


%\addtolength{\linewidth}{-1cm}
\begin{center}

\fbox{\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
{
{\LARGE \textbf{ABSTRACT.}}
{\LARGE
\talkabstract
}
}
\end{minipage}
\end{center}
%\vspace*{.35cm}
%\vspace*{.35cm}
}}

\end{center}
\end{document}
