\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\usepackage[none]{hyphenat} 

\setlength{\hoffset}{-.5in}%{-1in}
\addtolength{\hoffset}{1.5cm}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2\hoffset}
\addtolength{\textwidth}{-2in}

\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2in}%to fix pdf missing footer . old val {-.75in}
\setlength{\oddsidemargin}{-0.75cm}
\setlength{\marginparsep}{0cm}
\setlength{\marginparwidth}{0cm}
\setlength{\marginparpush}{0cm}
\addtolength{\textwidth}{-\oddsidemargin}
\addtolength{\textwidth}{-\marginparsep}
\addtolength{\textwidth}{-\marginparwidth}
\addtolength{\textwidth}{-\marginparpush}


\setlength{\voffset}{-.5in}%{-1in}
\addtolength{\voffset}{1cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2\voffset}
\addtolength{\textheight}{-1in}%to fix pdf missing footer . old val {-.75in}


%\textheight=700pt


\linespread{1.65}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Motion Encoding in Turtle Retina}
\newcommand{\talkspeaker}{ {\sc Mervyn P. B. Ekanayake
}, \textit{Texas Tech University}}

\newcommand{\talkdate}{Wednesday, April 27, 2011}

\newcommand{\timelocation}{Room: MATH 016.  Time: 4:00pm.}

\newcommand{\talkabstract}{
%\Large
Cellular level models of neural circuits provide an understanding of the complex neurological phenomena,
such as vision. Encoding visual inputs in the visual system of an animal depends on the cellular level properties
as well as cell distribution and interconnections in multiple stages. The Retina provides the sensory inputs to the
deeper parts of the visual system. Turtle retina is different from humans in cell types and the distribution.  The
turtle retina has cells which are sensitive to motion direction in addition light intensity. The cells are distributed
in such a way that highest cell density occurs along a line called the visual streak.  In this talk I wish to present
our work on developing a model retinal patch of a turtle retina and an analysis of encodability/decodability on
the model retinal patch. The individual cells are modeled as a two stage hybrid model. These model cells are
distributed on the model retinal patch according to the actual cell distributions. The encodability and decodability analysis is conducted assuming the population response is a stochastic process. 
}

\begin{document}

\thispagestyle{empty}

\begin{center}
{\Large
Texas Tech University.  Applied Mathematics Seminar.
}
\medskip

\textbf{\Huge {\uppercase{\talktitle}} }

{\Large
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}


%\addtolength{\linewidth}{-1cm}
\begin{center}

\fbox{\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
{
{\LARGE \textbf{ABSTRACT.}}
{\huge \talkabstract}
}
\end{minipage}
\end{center}
%\vspace*{.35cm}
%\vspace*{.35cm}
}}

\end{center}
\end{document}
