\documentclass[oneside]{amsart}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\usepackage[none]{hyphenat} 

\setlength{\hoffset}{-.5in}%{-1in}
\addtolength{\hoffset}{1.5cm}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2\hoffset}
\addtolength{\textwidth}{-2in}

\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2in}%to fix pdf missing footer . old val {-.75in}
\setlength{\oddsidemargin}{-0.75cm}
\setlength{\marginparsep}{0cm}
\setlength{\marginparwidth}{0cm}
\setlength{\marginparpush}{0cm}
\addtolength{\textwidth}{-\oddsidemargin}
\addtolength{\textwidth}{-\marginparsep}
\addtolength{\textwidth}{-\marginparwidth}
\addtolength{\textwidth}{-\marginparpush}


\setlength{\voffset}{-.5in}%{-1in}
\addtolength{\voffset}{1cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2\voffset}
\addtolength{\textheight}{-1in}%to fix pdf missing footer . old val {-.75in}


%\textheight=700pt


\linespread{1.65}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{On stabilization of solutions to nonlinear parabolic equations of the p-Laplace type}

\newcommand{\talkspeaker}{ {\sc Mikhail Surnachev}\\ \textit{Institute of Applied Mathematics, Russian Academy of Science}}

\newcommand{\talkdate}{Wednesday, October 24, 2012}

\newcommand{\timelocation}{Room: MATH 014.  Time: 4:00pm.}

\newcommand{\talkabstract}{

In this talk I am going to present our joint results with Prof. Vasily Zhikov (Vladimir State University) on stabilization of solutions to nonlinear parabolic equations of the p-Laplace type.
The first result is stabilization in the $L^2(\mathbb{R}^n)$ norm of solutions with $L^2(\mathbb{R}^n)$ initial data.
The second result, which is the central part of this talk, is a criterion of the uniform stabilization of bounded solutions. This criterion generalizes a widely known criterion for linear parabolic equations proved independently by V. Zhikov and S. Kamin in 1976. The statement of the criterion is very simple: "A bounded solution converges uniformly (w.r.t. the space variables) to zero as time goes to infinity if and only if the initial data has zero uniform mean."
}

\begin{document}

\thispagestyle{empty}

\begin{center}
{\Large
Texas Tech University.  Applied Mathematics Seminar.
}
\medskip

\textbf{\Huge {\uppercase{\talktitle}} }

{\Large
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}


%\addtolength{\linewidth}{-1cm}
\begin{center}

\fbox{\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}
{
\vspace*{.25cm}
{\LARGE \textbf{ABSTRACT.}}
{\huge \talkabstract}
\vspace*{.25cm}
}
\end{minipage}
\end{center}
}}

\end{center}
\end{document}
