\documentclass[oneside]{article}
\usepackage{amssymb,amsfonts}
\usepackage{amsthm}

\usepackage{hyperref}

\usepackage{fancyhdr}

\usepackage[none]{hyphenat} 
\usepackage[left=.75 in,top=.75 in,right=.75 in,bottom=.75 in,nohead]{geometry}

\pagestyle{fancy}
\lfoot{}
\cfoot{\url{http://www.math.ttu.edu/~lhoang/AnalysisSeminar/}}
%\cfoot{\textit{http:/$\!$/www.math.ttu.edu/$\!$\raise-1ex\hbox{{\Large\texttt{\char`\~}}}lhoang/AppliedMath/}}
\rfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\linespread{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\talktitle}{Models and analysis of fluid flows in heterogeneous porous media. Part II.}

\newcommand{\talkspeaker}{ \textbf{\sc Luan Hoang }\\ \textit{Texas Tech University}}

\newcommand{\talkdate}{\textbf{Monday, March 20, 2017}}

\newcommand{\timelocation}{\textbf{Room: MATH 010.  Time: 4:00pm.}}

\newcommand{\talkabstract}{
{\Large The most common equation to describe fluid flows in porous media is the Darcy law.  
However, this linear equation  is not valid in many situations, particularly, when the Reynolds number is large or very small.
}\\

{\Large 
In the first part of this talk, we survey the Forchheimer models and their generalizations for compressible fluids in heterogeneous porous media. The Forchheimer coefficients in this case are functions of the spatial variables.
We derive a parabolic equation for the pressure which is both singular/degenerate in the spatial variables, and degenerate in the pressure's gradient.
}\\

{\Large 
In the second part, we model different flow regimes, namely, pre-Darcy, Darcy and post-Darcy, which may be present in different portions of a porous medium. 
To study these complex flows, we use a single equation of motion to unify all three regimes. Several scenarios and models are then considered for  slightly compressible fluids. A nonlinear  parabolic equation for the pressure is derived, which is degenerate when the pressure's gradient is either small or large. 
}\\

{\Large 
We estimate the pressure and its gradient for all time in terms of the initial and boundary data. We also obtain their particular bounds for large time which depend on the asymptotic behavior of the boundary data but not on the initial one. Moreover, the continuous dependence of the solutions on  the initial and boundary data, and the structural stability for the equations are established.
}
%
}

\begin{document}

%\vspace*{-2cm}
\begin{center}
{\LARGE
Texas Tech University.  Analysis Seminars.
}
\medskip

\textbf{\Huge {\uppercase{\talktitle}} }

{\LARGE
\talkspeaker\\
\talkdate\\
\timelocation
}
\end{center}

\vspace*{10pt}


%\addtolength{\linewidth}{-1cm}
\begin{center}

\fbox{\parbox{\linewidth}{
\begin{center}
\begin{minipage}[c]{.96\linewidth}

\vspace*{.25cm}
{\LARGE \textbf{ABSTRACT.}}
\talkabstract
\vspace*{.25cm}

\end{minipage}
\end{center}
}}

\end{center}
\end{document}
